D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
"Inventing Atomic Loads": Reword
Also stomp out a couple more "implementations" that hid previous
efforts by virtue of being capitalized.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

First, consider Listing~\ref{lst:No Invented Atomic Loads}.
At first glance, this might appear straightforward.
\co{P0()}'s store to \co{z} clearly depends on its load from \co{y},
and \co{P1()}'s store to \co{y} clearly depends on its load from \co{z}.
If both dependencies are semantic dependency, the OOTA cycle cannot
form.

@@

\begin{enumerate}
\item	Listing~\ref{lst:No Invented Atomic Loads}
	looks like it has an OOTA cycle, but there is in fact no
	semantic dependency.
\item	Attempts to use real-world constraints to prevent OOTA cycles
	are futile.
\item	Implementations should not invent uses for values from
	nonvolatile relaxed atomic loads.
	If it turns out that there are useful optimizations that invent
	such uses, then such optimizations must be applied only with
	careful attention to the as-if rule.
	Some might argue that inventing comparisons between a pair of
	nonvolatile relaxed atomic loads from the same object should
	be permitted only if the two loads could be reordered to be
	adjacent to each other.
\item	Any time a compiler might be tempted to invent uses from
	values from nonvolatile relaxed atomic loads from the same
	object, the loads should instead be fused into a single load.
	This reaction might be attractive to those who carefully consider
	the pointlessness of keeping two loads that return the same value
	on the one hand or the cache-miss overhead incurred when closely
	spaced loads return different values on the other.
\item	Implementations that invent nonvolatile atomic loads or invent
	new uses for nonvolatile atomic loads can adversely affect
	observed behavior, for example, by introducing error into code
	attempting to do statistical sampling.
\item	What other interesting situations might come to light?
\end{enumerate}

@@

Note that passing \co{x} to the call to \co{do_something_with()} is important
because this allows the compiler to assume that accesses to \co{x}
will not result in a data race.
Without this assumption, the above transformation might introduce a data
race when \co{limit} is less than or equal to zero.

>>>>

First, consider Listing~\ref{lst:No Invented Atomic Loads}.
At first glance, this might appear straightforward.
\co{P0()}'s store to \co{z} clearly depends on its load from \co{y},
and \co{P1()}'s store to \co{y} clearly depends on its load from \co{z}.
If both dependencies are semantic dependencies, the OOTA cycle cannot
form.

@@

\begin{enumerate}
\item	Listing~\ref{lst:No Invented Atomic Loads}
	looks like it has an OOTA cycle, but there is in fact no
	semantic dependency.
\item	Attempts to use real-world constraints to prevent OOTA cycles
	are futile.
\item	Compilers should not invent uses for values from
	nonvolatile relaxed atomic loads.
	If it turns out that there are useful optimizations that invent
	such uses, then such optimizations must be applied only with
	careful attention to the as-if rule.
	Some might argue that inventing comparisons between a pair of
	nonvolatile relaxed atomic loads from the same object should
	be permitted only if the two loads could be reordered to be
	adjacent to each other.
\item	Any time a compiler might be tempted to invent uses from
	values from nonvolatile relaxed atomic loads from the same
	object, the loads should instead be fused into a single load.
	This reaction might be attractive to those who carefully consider
	the pointlessness of keeping two loads that return the same value
	on the one hand or the cache-miss overhead incurred when closely
	spaced loads return different values on the other.
\item	Compilers that invent nonvolatile atomic loads or invent
	new uses for nonvolatile atomic loads can adversely affect
	observed behavior, for example, by introducing error into code
	attempting to do statistical sampling.
\item	What other interesting situations might come to light?
\end{enumerate}

@@

Note that passing \co{x} to the call to \co{do_something_with()} is important
because this allows the compiler to assume that inventing additional
accesses to \co{x} will not result in a data race.
Without this assumption, the above transformation might introduce a data
race when \co{limit} is less than or equal to zero.
